---
title: "Untitled"
author: "Karim Primov"
date: "3/1/2022"
output: html_document
---

Challenge 1

Loading libraries 
```{r}
library(mosaic)
library(tidyverse)
library(ggplot2)
```

Loading in data 
```{r}
f <- "https://raw.githubusercontent.com/difiore/ada-2022-datasets/main/IMDB-movies.csv"
```

Filtering data to only include movies from 1920-1979
```{r}
d <- read_csv(f, col_names = TRUE) %>%
  filter(startYear %in% 1920:1979) %>% 
  filter(runtimeMinutes %in% 60:180)%>%
  mutate(decade = case_when(startYear <=1929 ~ "20's", 
                            startYear <=1939 & startYear >=1930 ~"30's",
                            startYear <=1949 & startYear >=1940 ~"40's",
                            startYear <=1959 & startYear >=1950 ~"50's",
                            startYear <=1969 & startYear >=1960 ~"60's",
                            startYear <=1979 & startYear >=1970 ~"70's"))
```

Get separate histograms for runtimes for each decade
```{r}
ggplot(data = d, aes(x = runtimeMinutes)) + 
  geom_histogram() + 
  facet_wrap(~decade)
```

one-line statement to calculate pop. mean and pop. std.dev in runtimeMinutes for each decade and save results in new df called "results"
```{r}
results <- group_by(d, decade) %>% 
  summarise(pop.mean = mean(runtimeMinutes, na.rm = TRUE), pop.std.dev = sd(runtimeMinutes, na.rm = TRUE))

results
```

Draw single sample of 100 movies w/o replacement
```{r}
no.replacement <- group_by(d, decade) %>% 
 sample_n(size = 100, replace = FALSE) %>%
  summarise(sample.mean = mean(runtimeMinutes, na.rm = TRUE), sample.std.dev = sd(runtimeMinutes, na.rm = TRUE)) %>%
  mutate(std.error.decade = sample.std.dev / sqrt(100))

no.replacement
```

Generating sampling distribution of mean runtimeMinutes
```{r}
sampdist.df <- data.frame(matrix(ncol = 6, nrow = 1000))
colnames(sampdist.df) <- no.replacement$decade
reps <- 1000
for (i in no.replacement$decade){
  samp.means.dist <- do(reps) * mean(~ runtimeMinutes, data = sample_n(filter(d, decade == i), size = 100, replace = FALSE))
  sampdist.df[[i]] <- samp.means.dist$mean
  print(histogram(sampdist.df [[i]]))
}

mean(sampdist.df) %>% group_by(decade)
```

Calculating mean and standard deviation of sampling distribution of sample means for each decade
```{r}


  

#mean.samp.dist <- sort(samp.dist$decade) %>% mean(samp.dist$mean, na.rm=TRUE)

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```


```{r}

```
